Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
classifier similarity

\noindent \textbf{Creating a validation corpus} --- For MySQL 3.23 and MaxDB 7.500, we manually annotated each extracted topic in each period with the same NFR labels as \textsf{exp2} (software qualities). 
We looked at each period's topics, and assessed what the data --- consisting of the frequency-weighted word lists and messages --- suggested was the topic for that period. 
We were able to pinpoint the appropriate label using auxiliary information as well, such as the actual revisions and files that were related to the topic being annotated.
For example, for the MaxDB topic consisting of a message ``exit() only used in non NPTL LINUX Versions'', we tagged that topic \emph{portability}. 
We compared against this data-set, but we also used it for our supervised machine learning based topic classification. 
% A topic may have more than one matching keyword. % ok what?
\todo[inline]{inter-rater reliability }
% \todo[inline]{There should be a section here which is about manual annotation. It is really important and it is required by both analyses. Plus we can tell them how.}

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers, the first layer determines if an entity should be labelled, while the second layer determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. 
These classifiers performed better than other multi-label classifiers. 
They have the best micro and macro ROC scores, although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
\todo[inline]{discuss this similarity in more detail}

>>>>

\noindent \textbf{Creating a validation corpus} --- For MySQL 3.23 and MaxDB 7.500, we manually annotated each extracted topic in each period with the same NFR labels as \textsf{exp2} (software qualities). 
We looked at each period's topics, and assessed what the data --- consisting of the frequency-weighted word lists and messages --- suggested was the topic for that period. 
We were able to pinpoint the appropriate label using auxiliary information as well, such as the actual revisions and files that were related to the topic being annotated.
For example, for the MaxDB topic consisting of a message ``exit() only used in non NPTL LINUX Versions'', we tagged that topic \emph{portability}. 
We compared against this data-set, but we also used it for our supervised machine learning based topic classification. 
% A topic may have more than one matching keyword. % ok what?
%\todo[inline]{inter-rater reliability }
% \todo[inline]{There should be a section here which is about manual annotation. It is really important and it is required by both analyses. Plus we can tell them how.}

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers, the first layer determines if an entity should be labelled, while the second layer determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. 
These classifiers performed better than other multi-label classifiers as they have the best micro and macro ROC scores. 
The multi-label and single-label learners had similar performance: for MySQL, BR and NaiveBayes had similar macro-ROC scores of $0.74$.
% although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
%\todo[inline]{discuss this similarity in more detail}
